The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-16 paper.tex
update

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg-CR.png}
    \caption{
     The CR pressure slice passing through the jet source at 12.39 Myr.\
     Comparison between\
     gas pressure (\Cref{fig__jetI5+ismSeed3-45deg}) and cosmic ray pressure\
     shows that
     the CR pressure\
     is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
     less than the gas pressure\
     by a factor of 10--20.\
     We thefore stress that\
     ignoring the contribution of CR pressure gradient to the momentum of the gas\
     in \Cref{governing-eq} is resonable.
     }
    \label{fig__jetI5+ismSeed3-45deg-CR}
  \end{figure}

>>>>

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg-CR.png}
    \caption{
     The CR pressure slice passing through the jet source at 12.39 Myr.\
     Comparison between\
     gas pressure (\Cref{fig__jetI5+ismSeed3-45deg}) and cosmic ray pressure\
     shows that
     the CR pressure\
     is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
     bringing the the pressure ratio of CR to gas is 0.1--0.2,
     similar to 0.18 at the begining of the simulation.
     We thefore stress that\
     ignoring the contribution of CR pressure gradient to the momentum of the gas\
     in \Cref{governing-eq} is resonable.
     }
    \label{fig__jetI5+ismSeed3-45deg-CR}
  \end{figure}
